---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countMissing

<!-- badges: start -->
<!-- badges: end -->

The goal of countMissing is to count missing values for all columns by group.

Given a data frame `data` and a column `group`, `count_all_missing_by_group()` creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`.

## Repository files

The file R/countMissing.R contains the source code.

The file test/testthat/test-countMissing.R contains the unit test codes.

The file man/count_all_missing_by_group.Rd contains the roxygen2 tags.

## Installation

You can install the development version of countMissing from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("yasmine-mcdonough/countMissing")
```

## Example

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column.

```{r example}
library(countMissing)
count_all_missing_by_group(airquality, Month)
```


